TODO LIST

### 2019-02-28 LMCS/sendrev/beyond.tex
Solving some pending issues of reviewer 1

\begin{exa} \label{ex:count-path}
We would like to define an $\rqfo(\fo)$-formula that, given a directed acyclic graph $G$ with $n$ nodes and a pair of nodes $b$, $c$ in $G$, counts the number of paths of length less than $n$ from $b$ to $c$ in $G$. To this end, assume that graphs are encoded using the signature $\R = \{ E(\cdot,\cdot)\}$, and then define formula $\alpha(x, y, f)$ as follows:
$$ 
E(x,y) + \sa{z} f(x,z)\cdot E(z,y).
$$
We have that $\clfp{\alpha(x,y,f)}$ defines our counting function. In fact, assume that $\A$ is an $\R$-structure with $n$ elements in its domain encoding an acyclic directed graph. Moreover, assume that $b,c$ are elements of $\A$ and $v$ is a first-order assignment over $\A$ such that $v(x) = b$ and $v(y) = c$. Then we have that $\sem{\clfp{\alpha(x,y,f)}}(\A,v)$ is equal to the number of paths in $\A$ from $b$ to $c$ of length at most $n-1$.

>>>>

\begin{exa} \label{ex:count-path}
We would like to define an $\rqfo(\fo)$-formula that, given a directed acyclic graph $G$ with $n$ nodes and a pair of nodes $b$, $c$ in $G$, counts the number of paths of length less than $n$ from $b$ to $c$ in $G$. To this end, assume that graphs are encoded using the signature $\R = \{ E(\cdot,\cdot),<\}$, and then define formula $\alpha(x, y, f)$ as follows:
$$ 
E(x,y) + \sa{z} f(x,z)\cdot E(z,y).
$$
We have that $\clfp{\alpha(x,y,f)}$ defines our counting function. In fact, assume that $\A$ is an $\R$-structure with $n$ elements in its domain encoding an acyclic directed graph. Moreover, assume that $b,c$ are elements of $\A$ and $v$ is a first-order assignment over $\A$ such that $v(x) = b$ and $v(y) = c$. Then we have that $\sem{\clfp{\alpha(x,y,f)}}(\A,v)$ is equal to the number of paths in $\A$ from $b$ to $c$ of length at most $n-1$.

### 2019-02-28 LMCS/sendrev/introduction.tex
un par de correcciones y algunos problemas de compatibilidad con el la instruccion !TEX = main
Solving some pending issues of reviewer 1

In this paper, we propose to study the descriptive complexity of counting complexity classes in terms of Weighted Logics (WL)~\cite{DrosteG07}, a general logical framework that combines Boolean formulae (e.g. in $\fo$ or $\so$) with operations over a fixed semiring (e.g. $\bbN$). 
Specifically, we propose to restrict WL to the natural numbers as a fixed semiring, calling this restriction Quantitative Second Order Logics (QSO), and study its expressive power for defining counting complexity classes over ordered structures. 
As a proof of concept, we show that natural syntactical fragments of $\qso$ captures counting complexity classes like $\shp$, $\spp$, $\fp$ and $\fpspace$.
Furthermore, by slightly extending the framework we can prove that $\qso$ can also capture classes like $\gp$ and $\optp$, showing the robustness of our approach.

>>>>

In this paper, we propose to study the descriptive complexity of counting complexity classes in terms of Weighted Logics (WL)~\cite{DrosteG07}, a general logical framework that combines Boolean formulae (e.g. in $\fo$ or $\so$) with operations over a fixed semiring (e.g. $\bbN$). 
Specifically, we propose to restrict WL to the natural numbers as a fixed semiring, calling this restriction Quantitative Second Order Logics (QSO), and study its expressive power for defining counting complexity classes over ordered structures. 
As a proof of concept, we show that natural syntactical fragments of $\qso$ capture counting complexity classes like $\shp$, $\spp$, $\fp$ and $\fpspace$.
Furthermore, by slightly extending the framework we can prove that $\qso$ can also capture classes like $\gp$ and $\optp$, showing the robustness of our approach.

### 2019-02-28 LMCS/sendrev/todo-list.tex
un par de correcciones y algunos problemas de compatibilidad con el la instruccion !TEX = main
Solving some pending issues of reviewer 1

\item[$\checkmark$] p.2, first paragraph: ``However, other function classes have emerged from the need to understand
the complexity of some computation problems for which little can be said if their
decision counterparts are considered.'' Why can only little be said about the decision counterparts
of the examples mentionend afterwards?
\item[$\checkmark$] p.7, first sentence: ``fragments or extensions [...] obtained by restricting'': extensions are not
obtained by restricting something
\item[$\checkmark$] p.10, before Thm. 4.5: ``by considering second-order product'': We need both second-order
product and sum (at least both are used in Thm. 4.5)
\item[$\checkmark$] p.10, last line: ``$B$-th bit'': mention in what way $B$ is interpreted as a number
\item[$\checkmark$] p.12: ``To formalize this set of optimization problems'': class instead of set
\item[$\checkmark$] p.14: ``we have to concentrate on the class of counting problems with easy decision versions'':
here, easy decision version means ``in \bpp''. Before, it was defined as ``in P''. Should be
consistent.
\item[$\checkmark$] p.14: ``as expected, $\Sigma \bar{X}$ is the respective nesting of $\Sigma X.$’s'': why is this explained for secondorder
quantifiers but not for first-order quantifiers?
\item[$\checkmark$] p.14: $\sum_{i=1}^n\alpha_i$: explain that this is notation for $\alpha_1+\cdots+\alpha_n$
\item[$\checkmark$] p.17: ``Since $\alpha$ is not null'' $\to$ ``Since $\sem{\alpha}$ is not the identically zero function'' (or similar)
\item[$\checkmark$] p.17/18: In the proof of Prop 5.3, the vocabulary only contains the numerical predicate $<$. When encoding structures as binary words, numerical predicates are implicit (and not
encoded), though. What is the intended meaning here?
\item[$\checkmark$] p.18, after proof of Claim 5.4: ``which implies that 2 $\in \eqso(\Sigma_0)$ and $2 \not\in \E{1}$'': $2 \in \eqso(\Sigma_0)$
does not follow from the argument before as stated in this sentence, but is trivial
\item[$\checkmark$] p.18: ``Also, suppose that it is in $\L$-PNF'': $\L$ should be $\LL$ , PNF should be SNF
\item[$\checkmark$] p.19, end of proof of Prop. 5.5: ``which violates the inequality'' $\to$ ``which violates the inequality
for large structures''
\item[$\checkmark$] p.20: ``we will show a formula in the grammar'' $\to$ ``... in the logic''
\item[$\checkmark$] p.20: ``Since $\Sigma_1$ is closed under conjunction, then Lemma 5.7 holds for ...'' $\to$ ``Since $\Sigma_1$ is
closed under cnojunction, Lemma 5.7 can be applied to ...'' (or similar)
\item[$\checkmark$] p.22: ``and leaving each $R_{\psi}^{\A}$ empty'' $\to$ $R_{\psi}^{\A'}$
\item[$\checkmark$] p.22: ``To show that $\alpha$ is in \totp'' $\to$ ``To show that the function defined by $\alpha$ ...'' (or similar)
\item[$\checkmark$] p.22: ``Let $\alpha$ = ... where $\varphi$ is an FO-formula'' $\to$ ``... where $\varphi$ is an $\Sigma_1$[FO]-formula''
\item[$\checkmark$] p.23, formulae: Maybe put (large) parantheses around the relativization of quantifiers, for
example the part of formula $\varphi_i$ after the quantifiers
\item[$\checkmark$] p.24, formula 5.6: subscript of large conjunction: $\varphi_i^{+}(\bar{X},\bar{v})$ $\to$ $\varphi_i^{+}(\bar{X},\bar{y})$
\item[$\checkmark$] p.25: ``We construct a function $\lambda$ that receives a quantitative formula $\beta$ ...'' $\to$ ``... that receives
a formula $\beta \in \eqso(\logex{1})$ ...''
\item p.25, last sentence: ``which is based on considering some witnesses of logarithmic size'' could
be explained a little more / made more clear
\martin{no logr\'e completar esta correcci\'on}

@@

	\item throughout the paper: plural used with verb ending on s. Examples:

@@

	\item[-] p.2, middle: ``fragments of QSO captures''
	\item[-] p.6, example 3.1: ``the sum quantifiers in $\alpha_1$ aggregates''

@@

@@

	\item throughout the paper: singular used with verb not ending on s. Examples:

@@

	\item[-] p.9, after proof of Prop. 4.3: ``use of a fragment [...] that capture''
	\item[-] p.11, end of proof of Thm. 4.5: ``and $\alpha$ reconstruct''

@@

@@

	\item In [1], a similar hierarchy to the one by Saluja et al. was introduced and studied. This work should be cited.

@@

>>>>

\begin{itemize}
	\setlength\itemsep{0.5em}
\item[$\checkmark$] p.2, first paragraph: ``However, other function classes have emerged from the need to understand
the complexity of some computation problems for which little can be said if their
decision counterparts are considered.'' Why can only little be said about the decision counterparts
of the examples mentionend afterwards?
\item[$\checkmark$] p.7, first sentence: ``fragments or extensions [...] obtained by restricting'': extensions are not
obtained by restricting something
\item[$\checkmark$] p.10, before Thm. 4.5: ``by considering second-order product'': We need both second-order
product and sum (at least both are used in Thm. 4.5)
\item[$\checkmark$] p.10, last line: ``$B$-th bit'': mention in what way $B$ is interpreted as a number
\item[$\checkmark$] p.12: ``To formalize this set of optimization problems'': class instead of set
\item[$\checkmark$] p.14: ``we have to concentrate on the class of counting problems with easy decision versions'':
here, easy decision version means ``in \bpp''. Before, it was defined as ``in P''. Should be
consistent.
\item[$\checkmark$] p.14: ``as expected, $\Sigma \bar{X}$ is the respective nesting of $\Sigma X.$’s'': why is this explained for secondorder
quantifiers but not for first-order quantifiers?
\item[$\checkmark$] p.14: $\sum_{i=1}^n\alpha_i$: explain that this is notation for $\alpha_1+\cdots+\alpha_n$
\item[$\checkmark$] p.17: ``Since $\alpha$ is not null'' $\to$ ``Since $\sem{\alpha}$ is not the identically zero function'' (or similar)
\item[$\checkmark$] p.17/18: In the proof of Prop 5.3, the vocabulary only contains the numerical predicate $<$. When encoding structures as binary words, numerical predicates are implicit (and not
encoded), though. What is the intended meaning here?
\item[$\checkmark$] p.18, after proof of Claim 5.4: ``which implies that 2 $\in \eqso(\Sigma_0)$ and $2 \not\in \E{1}$'': $2 \in \eqso(\Sigma_0)$
does not follow from the argument before as stated in this sentence, but is trivial
\item[$\checkmark$] p.18: ``Also, suppose that it is in $\L$-PNF'': $\L$ should be $\LL$ , PNF should be SNF
\item[$\checkmark$] p.19, end of proof of Prop. 5.5: ``which violates the inequality'' $\to$ ``which violates the inequality
for large structures''
\item[$\checkmark$] p.20: ``we will show a formula in the grammar'' $\to$ ``... in the logic''
\item[$\checkmark$] p.20: ``Since $\Sigma_1$ is closed under conjunction, then Lemma 5.7 holds for ...'' $\to$ ``Since $\Sigma_1$ is
closed under cnojunction, Lemma 5.7 can be applied to ...'' (or similar)
\item[$\checkmark$] p.22: ``and leaving each $R_{\psi}^{\A}$ empty'' $\to$ $R_{\psi}^{\A'}$
\item[$\checkmark$] p.22: ``To show that $\alpha$ is in \totp'' $\to$ ``To show that the function defined by $\alpha$ ...'' (or similar)
\item[$\checkmark$] p.22: ``Let $\alpha$ = ... where $\varphi$ is an FO-formula'' $\to$ ``... where $\varphi$ is an $\Sigma_1$[FO]-formula''
\item[$\checkmark$] p.23, formulae: Maybe put (large) parantheses around the relativization of quantifiers, for
example the part of formula $\varphi_i$ after the quantifiers
\item[$\checkmark$] p.24, formula 5.6: subscript of large conjunction: $\varphi_i^{+}(\bar{X},\bar{v})$ $\to$ $\varphi_i^{+}(\bar{X},\bar{y})$
\item[$\checkmark$] p.25: ``We construct a function $\lambda$ that receives a quantitative formula $\beta$ ...'' $\to$ ``... that receives
a formula $\beta \in \eqso(\logex{1})$ ...''
\item[$\checkmark$] p.25, last sentence: ``which is based on considering some witnesses of logarithmic size'' could
be explained a little more / made more clear
\marcelo{Esto quedo listo con el ejemplo que puso Martin y la pasada que hice sobre el}

@@

	\item[$\checkmark$] throughout the paper: plural used with verb ending on s. Examples:

@@

	\item[$\checkmark$] p.2, middle: ``fragments of QSO captures''
	\item[$\checkmark$] p.6, example 3.1: ``the sum quantifiers in $\alpha_1$ aggregates''

@@

	\marcelo{corregi estos errores en el paper}

@@

	\item[$\checkmark$] throughout the paper: singular used with verb not ending on s. Examples:

@@

	\item[$\checkmark$] p.9, after proof of Prop. 4.3: ``use of a fragment [...] that capture''
	\item[$\checkmark$] p.11, end of proof of Thm. 4.5: ``and $\alpha$ reconstruct''

@@

	\marcelo{tambien corregi esto}

@@

	\item In \cite{DBLP:conf/csl/0001HKV16}, a similar hierarchy to the one by Saluja et al. was introduced and studied. This work should be cited.

@@

\bibliographystyle{plain}
\bibliography{0001HKV16}
